---
title: "Reproduce Results From Fujikawa et al. (2022)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reproduce_Fujikawa}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this vignette we show how to reproduce the results from Fujikawa et al. (2020) using `baskexact`. At first, we have to set up a a design object, using either `setupOneStageBasket()` for a single-stage design or `setupTwoStageBasket()`for a two-stage design with one interim analysis.

```{r setup, eval=FALSE}
library(baskexact)
design1 <- setupOneStageBasket(k = 3, shape1 = 1, shape2 = 1, p0 = 0.2)
```

To get the results shown in Figure 1, `basket_test()` can be used, which computes posterior probabilities for a given results-vector and also shows the pairwise weights and the parameters of the Beta posterior distribution.

```{r, eval=FALSE}
basket_test(design1, n = 15, r = c(1, 5, 7), lambda = 0.99, 
  weight_fun = weights_fujikawa, weight_params = list(epsilon = 2, tau = 0.5,
    logbase = exp(1)))
```

Note that at the moment it's not possible to reproduce the results from Table 1, as `baskexact` currently doesn't support baskets with unequal sample sizes.

To reproduce the results from Table 2 we can use `toer()` and `pow()`. First, the results from the single-stage design with two different choices of tuning parameter values. Fujikawa et al.'s "Proposed design (i)" uses $\varepsilon = 2$ and $\tau = 0$, "Proposed design (ii)" uses $\varepsilon = 2$ and $\tau = 0.5$.

Note that the default value for the logbase parameter is 2, such that the weights are always bounded between 0 and 1, but Fujikawa et al. use the natural logarithm, which leads to a lower limit for the weights that is strictly greater than 0.

```{r, eval=FALSE}
## p = (0.2, 0.2, 0.2)
# Proposed design (i)
toer(
  design = design1, n = 24, lambda = 0.99,
  weight_fun = weights_fujikawa, weight_params = list(epsilon = 2, tau = 0,
  logbase = exp(1)), results = "group"
)

# Proposed design (ii)
toer(
  design = design1, n = 24, lambda = 0.99,
  weight_fun = weights_fujikawa, weight_params = list(epsilon = 2, tau = 0.5,
  logbase = exp(1)), results = "group"
)
```

For the results from the two-stage design, we have to set up a different design object at first:

```{r, eval=FALSE}
design2 <- setupTwoStageBasket(k = 3, shape1 = 1, shape2 = 1, p0 = 0.2)
```

Fujikawa et al. use an interim analysis that allows stopping of individual baskets based on the posterior predictive probability.

```{r, eval = FALSE}
## p = (0.2, 0.2, 0.2)
# Proposed design (i)
toer(
  design = design2, n = 24, n1 = 15, lambda = 0.99, 
  interim_fun = interim_postpred, interim_params = list(prob_futstop = 0.1,
    prob_effstop = 0.9), weight_fun = weights_fujikawa,
  weight_params = list(logbase = exp(1), tau = 0, epsilon = 2),
  results = "group"
)

# Proposed design (ii)
toer(
  design = design2, n = 24, n1 = 15, lambda = 0.99, 
  interim_fun = interim_postpred, interim_params = list(prob_futstop = 0.1,
    prob_effstop = 0.9), weight_fun = weights_fujikawa,
  weight_params = list(logbase = exp(1), tau = 0.5, epsilon = 2),
  results = "group"
)

## p = c(0.5, 0.2, 0.2)
# Proposed design (i)
pow(
  design = design2, p1 = c(0.5, 0.2, 0.2), n = 24, n1 = 15, lambda = 0.99, 
  interim_fun = interim_postpred, interim_params = list(prob_futstop = 0.1,
    prob_effstop = 0.9), weight_fun = weights_fujikawa,
  weight_params = list(logbase = exp(1), tau = 0, epsilon = 2),
  results = "group"
)

# Proposed design (ii)
pow(
  design = design2, p1 = c(0.5, 0.2, 0.2), n = 24, n1 = 15, lambda = 0.99, 
  interim_fun = interim_postpred, interim_params = list(prob_futstop = 0.1,
    prob_effstop = 0.9), weight_fun = weights_fujikawa,
  weight_params = list(logbase = exp(1), tau = 0.5, epsilon = 2),
  results = "group"
)

## p = c(0.5, 0.5, 0.2)
# Proposed design (i)
pow(
  design = design2, p1 = c(0.5, 0.5, 0.2), n = 24, n1 = 15, lambda = 0.99, 
  interim_fun = interim_postpred, interim_params = list(prob_futstop = 0.1,
    prob_effstop = 0.9), weight_fun = weights_fujikawa,
  weight_params = list(logbase = exp(1), tau = 0, epsilon = 2),
  results = "group"
)

# Proposed design (ii)
pow(
  design = design2, p1 = c(0.5, 0.5, 0.2), n = 24, n1 = 15, lambda = 0.99, 
  interim_fun = interim_postpred, interim_params = list(prob_futstop = 0.1,
    prob_effstop = 0.9), weight_fun = weights_fujikawa,
  weight_params = list(logbase = exp(1), tau = 0.5, epsilon = 2),
  results = "group"
)

## p = c(0.5, 0.5, 0.5)
# Proposed design (i)
pow(
  design = design2, p1 = c(0.5, 0.5, 0.5), n = 24, n1 = 15, lambda = 0.99, 
  interim_fun = interim_postpred, interim_params = list(prob_futstop = 0.1,
    prob_effstop = 0.9), weight_fun = weights_fujikawa,
  weight_params = list(logbase = exp(1), tau = 0, epsilon = 2),
  results = "group"
)

# Proposed design (ii)
pow(
  design = design2, p1 = c(0.5, 0.5, 0.5), n = 24, n1 = 15, lambda = 0.99, 
  interim_fun = interim_postpred, interim_params = list(prob_futstop = 0.1,
    prob_effstop = 0.9), weight_fun = weights_fujikawa,
  weight_params = list(logbase = exp(1), tau = 0.5, epsilon = 2),
  results = "group"
)
```

Note that the results are slightly different, as Fujikawa et al.'s results are based on simulation with $n_{\text{sim}} = 5000$. `baskexact` calculates the results analytically.

## References
Fujikawa, K., Teramukai, S., Yokota, I., & Daimon, T. (2020). A Bayesian basket trial design that borrows information across strata based on the similarity between the posterior distributions of the response probability. Biometrical Journal, 62(2), 330-338.
